% !TEX root = ../main.tex

\chapter{Structure}
\label{ch:structure}


% TODO subchapters recap
% Giving a recap of what has already happened first
The first part of this thesis was to state the motivation,
establish a theory and the goals of this thesis, and introduce the technologies that will be used.
\par
A definition of social media was made,
some examples of social media were introduced and compared,
and the growth and its impact quantified.
\par
Afterwards, theories stating that social media is not used to its full potential by companies and other entities,
and that it provide more value with the right tools and knowledge, were developed. \\
More specifically, it was theorized that monitoring sentiment and topics in real-time could, for example,
be used to detect and react to drastic moodshifts called shitstorms, or as a feedback mechanism during product development.
\par
The goal of this thesis was set to be to create a solution that enables people with varying technical prowess to monitor
which topics social media users are talking about and how they feel about these topics in real-time.
\par
Technologies that will be used to achieve this task were introduced, among them the language of choice for this thesis,
Python, as well as frameworks and libraries that will be used for modeling, analysis and streaming like the NLTK or Spark,
and the project structure was established and explained.
\par
% TODO subchapter outlook (or some other opposite of recap)
After giving a general introduction, the thesis will now go into the specific use-case that will be focused.
\par
Since this thesis will focus on Twitter as a easily accessible and analyzable medium,
it will be introduced, evaluated and explored in-depth both from a user and a technological perspective in the next chapter.
Also, the datasets used in the~\ref{ch:sentimentAnalysis} and~\ref{ch:topicModeling} will be created and explained.
\par
Then, sentiment analysis will be introduced and applied to data from Twitter.
Several different methods of sentiment analysis will be applied to different datasets.
They will be evaluated, quantified and compared, and a decision on which method is best-suited for this use-case will be made.
\par
The same will then be done with topic modeling.
\par
As the most important part of this thesis, the two will then be combined and the results evaluated,
by which point the value this combination will provide for the previously established stakeholders will be first discussed.
\par
To satisfy the requirement of enabling users from all disciplines to benefit from this combination,
a web-based dashboard is build that can be used to perform topic modeling and sentiment analysis on a
wide variety of easily configurable streams from Twitter, and that will visualize these and the combination of the two in an intuitive fashion.
\par
Lastly, the results of this thesis are reiterated, and a conclusion is drawn.
Open source contributions that were made during this thesis will be elaborated on,
and opportunities for future work on the subject will be discussed.
